Chemically Selective Transport in a Cross-linked H\textsubscript{II} Phase Lyotropic Liquid Crystal Membrane

### 2019-05-08 Ben_Manuscripts/transport/cover_letter.tex
updated tex.

	In this article, we use molecular dynamics (MD) simulations in order to observe 
	transport of small solutes in an inverted hexagonal (H\textsubscript{II}) phase 
	self-assembled lytropic liquid crystal (LLC) polymer membrane. Recently, we 
	published our first article on this subject in which we built and characterized
	an atomistic molecular model of an LLC membrane that is maximally consistent with experimental
	observations. By observing transport of solutes within a similar model, we can 
	learn the optimal ways to tune the shape, size and chemical functionality
	of LC monomers in order to intelligently design the pore environment and facilitate
	solute-specific separations.

	In this work, we observe and quantify transport of water, sodium and 20 small
	polar solutes within the pores of our atomistic H\textsubscript{II} phase LLC membrane
	model. In general, all solutes exhibit subdiffusive transport behavior
	characterized by intermittent hops between long periods of entrapment. However, 
	due the pores' inhomogeneous architecture, we observed 3 different mechanisms
	of entrapment. First, solutes can diffuse out of the pores and become entangled 
	between tails. Second, many of the solutes are capable of donating hydrogen bonds
	to monomer head groups for extended periods of time. Finally, solutes can associate
	with monomer head group counter-ions within nanopores. Each solute is influenced 
	by each mechanism to varying degrees dependent on its size and chemical 
	functionality. We begin our discussion with a broad description of these mechanisms
	in the context of all solutes before restricting the discussion to more detailed 
	analyses of subsets of chemically-similar solutes.

@@

		\item Francisco Hung has used molecular simulations to study nematic liquid crystals
		and various	nanostructured materials (Northeastern Univerity, 617-373-8619 	
		\href{mailto:f.hung@northeastern.edu}{f.hung@northeastern.edu})

>>>>

	In this article, we use molecular dynamics (MD) simulations in
        order to observe transport of small solutes in an inverted
        hexagonal (H\textsubscript{II}) phase self-assembled lytropic
        liquid crystal (LLC) polymer membrane. This is one of the
        first, and far the most extensive, uses of molecular dynamics
        to understand the molecular details of transport in such
        chemical complex nanostructured channels. Most importantly, we
        show how such channels can give rise to selective transport
        that is not simply size dependent, but also varies according
        to chemical functionality of the solutes.

        Recently, we characterized an atomistic molecular model of an
        LLC membrane that is maximally consistent with experimental
        observations (Coscia et al. \textit{J. Phys. Chem. B}, 123,
        289--309 (2019)). In this work, we observe and quantify
        transport of water, sodium and 20 small polar solutes within
        the pores of our atomistic H\textsubscript{II} phase LLC
        membrane model. In general, all solutes exhibit subdiffusive
        transport behavior characterized by intermittent hops between
        long periods of entrapment. However, due the pores'
        inhomogeneous architecture, we observed 3 different mechanisms
        of entrapment. First, solutes can diffuse out of the pores and
        become entangled between tails. Second, many of the solutes
        are capable of donating hydrogen bonds to monomer head groups
        for extended periods of time. Finally, solutes can associate
        with monomer head group counter-ions within nanopores. Each
        solute is influenced by each mechanism to varying degrees
        dependent on its size and chemical functionality. We begin our
        discussion with a broad description of these mechanisms in the
        context of all solutes before restricting the discussion to
        more detailed analyses of subsets of chemically-similar
        solutes.

@@

		\item Francisco Hung has used molecular simulations to study nematic liquid crystals
		and various	nanostructured materials (Northeastern University, 617-373-8619 	
		\href{mailto:f.hung@northeastern.edu}{f.hung@northeastern.edu})
